Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2019-11-08 paper.tex
Fixed figures to make them different from previous submissions

The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango} and \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities. 
It also provides access to Android's full range of interface tools and I/O options. 
Furthermore, a set of bone-conduction headphones (pictured in \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:tango}\includegraphics[width=0.4\columnwidth]{figures/tango_asus.jpeg}}
~
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.3\columnwidth]{figures/tango_headphone.png}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.2\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the latest Tango mobile phone (left), the former Tango tablet and the bone-conduction headphones used in this work (centre), and a participant with visual impairments during an experiment (right)~\citep{lock2019bone}.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
\hfil
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis~\citep{lock2019bone}.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}.}\label{fig:pipeline}
\end{figure}

>>>>

The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities. 
It also provides access to Android's full range of interface tools and I/O options. 
Furthermore, a set of bone-conduction headphones (pictured in \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.6\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.3\columnwidth]{figures/vi_participant.pdf}}
  \caption{Pictures of the former Tango tablet and the bone-conduction headphones used in this work (left), and a participant with visual impairments during an experiment (right)~\citep{lock2019bone}.}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
\end{figure}
